Demonstration of matching route networks

### 2024-02-14 r/demo.qmd
Update demo

Here are the examples of an intersection road.

>>>>

## Minimal example

A minimal example can be seen below:

```{r}
# setup input dataset:
x = sf::read_sf("data-raw/geojson/princes_street_minimal_x_1.geojson") |>
  sf::st_transform(27700)
y = sf::read_sf("data-raw/geojson/princes_street_minimal.geojson") |>
  sf::st_transform(27700)
x = x[3, ]
y = y[2:3, ]
matches <- rnetmatch::rnet_match(x, y, dist_tolerance = 10, angle_tolerance = 5)
y_aggregated <- rnet_aggregate(x, y, matches, value)
y_joined <- cbind(x, y_aggregated)
y_joined
x_segmented = stplanr::line_segment(x, segment_length = 10)
matches <- rnetmatch::rnet_match(x_segmented, y, dist_tolerance = 10, angle_tolerance = 5)
y_joined_segmented <- rnet_aggregate(x_segmented, y, matches, value)
sum(y_joined_segmented$value) # 
```

```{r}
funs = list(value = sum)
# With stplanr:
rnet_merged = stplanr::rnet_merge(x, y, dist = 10, funs = funs, max_angle_diff = 5, sum_flows = FALSE)
rnet_merged_segmented = stplanr::rnet_merge(x_segmented, y, dist = 10, funs = funs, max_angle_diff = 5, sum_flows = FALSE)
rnet_merged$value
rnet_merged_segmented$value
```

## Intersection example

This is where the rnet_merge function struggles to handle the intersection road.
